Supplementary Materials

### 2018-12-17 paper/paper.tex
Added hierarchical cluster analysis to paper

	\subsection{Cluster Analysis}
	We next sought to cluster the points, as a first step towards identifying ``prolific" authors. Because finding the number of clusters in such high dimensional data is difficult, we chose to use two different algorithms--DBSCAN (Density-Based Spatial Clustering of Applications with Noise)\cite{ester1996density} and mean-shift clustering \cite{comaniciu2002mean} from Python's sklearn package \cite{scikit-learn}. We picked two subsets of the data to perform this analysis on--the first was the set of variables that were highly correlated with \textit{v4} (denote this subset as $S_1$)--we chose these because it had an especially high number of correlated variables--and the second was the subset discussed in the previous subsection (which we shall denote as $S_2$. We also performed the clustering analysis with DBSCAN using PCA instead of manually picking features. The results of that are discussed in the Supplementary Materials.

>>>>

	\subsection{Cluster Analysis}
	Clustering provides an intuitive mechanism for identifying ``prolific" authors. We performed two kinds of clustering--hierarchical and density-based, which are detailed below.

	\subsubsection{Hierarchical Cluster Analysis}
	We first ran a Principal Components Analysis (PCA). Due to the highly correlated nature of the variables, we performed an oblique rotation (OBLIMIN). We conducted this analysis on a revised dataset that contained only performance indicators, and removed two unrelated features: \textit{Years} and \textit{Authors per Paper}. This resulted in three dimensions. A scree plot and a table showing the loadings of the original variables on the principal factors (after rotation) are given in the Supplementary Materials.

	We weighted each factor by the fraction of variables loaded on them; for example, the factor $D_1$ has a weight $\frac{19}{24}$ because of the 24 variables, the loading of 19 of the variables was maximum on $D_1$. Finally, we performed agglomerative hierarchical clustering on the projections of the variables, using the weights calculated. Figure 6 shows the dendogram obtained.

	\includegraphics[scale=0.35]{dendogram.png}
	\begingroup
	\captionof{figure}{Agglomerative hierarchical clustering dendogram}
	\endgroup
	\hfill\break

	\subsubsection{Density-Based Cluster Analysis}
	Because finding the number of clusters in such high dimensional data is difficult, we chose to use two different algorithms--DBSCAN (Density-Based Spatial Clustering of Applications with Noise)\cite{ester1996density} and mean-shift clustering \cite{comaniciu2002mean} from Python's sklearn package \cite{scikit-learn}. We picked two subsets of the data to perform this analysis on--the first was the set of variables that were highly correlated with \textit{v4} (denote this subset as $S_1$)--we chose these because it had an especially high number of correlated variables--and the second was the subset discussed in the previous subsection (which we shall denote as $S_2$. We also performed the clustering analysis with DBSCAN using PCA instead of manually picking features. The results of that are discussed in the Supplementary Materials.

### 2018-12-17 paper/supp.tex
Added hierarchical cluster analysis to paper

\subsection{PCA}
We performed a PCA before using DBSCAN. In all cases, we used the same method discussed in the paper to compute the value of \textit{eps}. We did this analysis for one through twelve dimensions. For number of dimensions greater than six, the performance stagnates at 0.571. We argue however, that the new dimensions obtained by PCA are less interpretable than simply using the original features, and the maximum difference between the performance of DBSCAN using our hand-picked features (0.571) and using PCA (0.644, n=2) was only 0.073. Figure 17 shows the results of using PCA to various numbers of dimensions.

@@

\subsection{Analysis on $S_1$}
Figure 18 shows the analysis for $S_1$. The Silhouette score for DBSCAN here was 0.635.

@@

\subsection{Analysis on $S_2$}
Figure 19 shows the analysis for $S_2$. As noted in the paper, the Silhouette score for DBSCAN for this subset was 0.571. \\

>>>>

\subsection{Agglomerative Clustering}
The scree plot for the variables is shown in Figure 17.

\includegraphics[scale=0.6]{scree.png}
\begingroup
\captionof{figure}{Scree Plot}
\endgroup
\hfill\break

The factor loadings after performing a PCA with OBLIMIN rotation are shown in Table 4.

\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Variable} & \textbf{F1} & \textbf{F2} & \textbf{F3}\\
\hline
Papers & \textbf{0.898} & -0.444 & -0.020\\
\hline
Citations & \textbf{0.919} & 0.023 & -0.157\\
\hline
Cites per Year & \textbf{0.834} & 0.287 & -0.076\\
\hline
Cites per Paper & 0.397 & \textbf{0.671} & 0.170\\
\hline
Cites per Author & \textbf{0.923} & 0.100 & -0.157\\
\hline
Papers per Author & \textbf{0.887} & -0.450 & -0.023\\
\hline
h-index & \textbf{0.964} & -0.079 & 0.111\\
\hline
g-index & \textbf{0.936} & 0.016 & 0.120\\
\hline
hc-index & \textbf{0.859} & 0.019 & 0.215\\
\hline
hI-index & \textbf{0.850} & 0.002 & 0.126\\
\hline
hI-norm & \textbf{0.924} & 0.001 & 0.148\\
\hline
AWCR & \textbf{0.903} & 0.062 & -0.090\\
\hline
AW-index & \textbf{0.885} & 0.067 & 0.169\\
\hline
AWCRpA & \textbf{0.921} & 0.145 & -0.094\\
\hline
e-index & \textbf{0.837} & 0.208 & 0.142\\
\hline
hm-index & \textbf{0.960} & -0.108 & 0.069\\
\hline
CitesAuthorYear & \textbf{0.785} & 0.397 & -0.089\\
\hline
CitesAuthorArticle & 0.331 & \textbf{0.734s} & 0.105\\
\hline
CitesAuthorYearArticle & -0.032 & \textbf{0.832} & 0.169\\
\hline
hI-annual & \textbf{0.455} & 0.322 & 0.362\\
\hline
h-coverage & -0.051 & 0.075 & \textbf{0.943}\\
\hline
g-coverage & 0.029 & -0.003 & \textbf{0.964}\\
\hline
Star count & \textbf{0.781} & 0.286 & -0.140\\
\hline
Adjusted star count & \textbf{0.722} & 0.425 & -0.146\\
\hline
\end{tabular}
\begingroup
\captionof{table}{Factor loadings after PCA. The factors that the variables are loaded on to are shown in bold for each variable.}
\endgroup

\subsection{PCA}
We performed a PCA before using DBSCAN. In all cases, we used the same method discussed in the paper to compute the value of \textit{eps}. We did this analysis for one through twelve dimensions. For number of dimensions greater than six, the performance stagnates at 0.571. We argue however, that the new dimensions obtained by PCA are less interpretable than simply using the original features, and the maximum difference between the performance of DBSCAN using our hand-picked features (0.571) and using PCA (0.644, n=2) was only 0.073. Figure 18 shows the results of using PCA to various numbers of dimensions.

@@

\subsection{Analysis on $S_1$}
Figure 19 shows the analysis for $S_1$. The Silhouette score for DBSCAN here was 0.635.

@@

\subsection{Analysis on $S_2$}
Figure 20 shows the analysis for $S_2$. As noted in the paper, the Silhouette score for DBSCAN for this subset was 0.571. \\
